Vasseur \& Fox (2007) replication

### 2022-12-14 report/project_definition.Rmd
Add simulations with some modules

@@

Interestingly, I see two schools on the definition of interaction strengths in
the Bioenergetic model. McCann defines it by modulating consumer preference
($\omega$) such as $I_{ki} = \omega_{ik}* x_i * y_i / B_{0i}$ while
@brose_allometric_2006 modules interaction strength by modulating predator/prey
mass ratios (Z) such as Z decrease the metabolism of predators
relative to prey (i.e. $x_i$ and $y_i$). Thus increasing Z decreases $I_{ki}$.
A common feature of both approaches is that they both consider that the strength
of interactions decrease as the trophic level increases.

@@

Although in complex food-webs, Brose method can create strong asymetry in
interaction strength by coupling specialists and generalists, as they
respectively generate strong and weak interactions. Such mechanism is
triggered by the fact that consumer preference is equally shared among preys
($\omega_ki = 1 \ \sum_k 1 $, such as $\omega_{ki} = 1$ or .1 for a consumer
having one prey or 10 preys).

@@

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE,
  fig.path="figures/"
)
```

@@

Interestingly, I see two schools on the definition of interaction strengths in
the Bioenergetic model. McCann defines it by modulating consumer preference
($\omega$) such as $I_{ki} = \omega_{ik} x_i  y_i / B_{0i}$ while
@brose_allometric_2006 modules interaction strength by modulating predator/prey
mass ratios (Z) such as Z decrease the metabolism of predators
relative to prey (i.e. $x_i$ and $y_i$). Thus increasing Z decreases $I_{ki}$.
A common feature of both approaches is that they both consider that the strength
of interactions decrease as the trophic level increases.

@@

Although in complex food-webs, Brose method can create strong asymetry in
interaction strength by coupling specialists and generalists, as they
respectively generate strong and weak interactions. Such mechanism is
triggered by the fact that consumer preference is equally shared among preys
($\omega_{ki} = 1 \ \sum_k 1$, such as $\omega_{ki} = 1$ or .1 for a consumer
having one prey or 10 preys).

@@

## Module and stability

```{r}
PlotWeb <- function (TL, webTL,colnode,abund,collink="grey70", scale_abun = 0.01, rel_abun = TRUE, log_abun = FALSE){

  Sweb<-length(TL)
  g=matrix(0,nrow=Sweb,ncol=3)

  if (log_abun) {
    # to not have negative abun:
    if(any(abund < 1)) {
      abund <- abund + 1
    }
    abund <- log(abund)

  }

  if (rel_abun) {
    g[,3]<- scale_abun * abund / sum(abund)
  } else {
    g[,3]<- scale_abun * abund
  }
  g[,2]<-TL/sum(TL)
  TLround<-round(TL)
  for (i in 1:max(round(TL))) {
    a<-TLround==i
    b<-1:Sweb
    b<-b[a]
    xaxis<-(1:length(b))/length(b)
    g[a,1]<-xaxis+ 0.5 - sum(xaxis)/length(b)
  }
  symbols(g[,1],g[,2],circles=g[,3],inches=FALSE,bg=colnode,fg=colnode,xlab="",ylab="",bty="n",xaxt="n",yaxt="n")
  for (i in 1:Sweb){
    for (j in 1:Sweb){
      if (webTL[i,j]>0){
         arrows(g[i,1],g[i,2],g[j,1],g[j,2],lwd=1, col=collink,length=0)
         }
    }
  }
  symbols(g[,1],g[,2],circles=g[,3],inches=FALSE,bg=colnode,fg=colnode,add=TRUE)
}
```

```{r, fig.width = 12}
null_mat <- matrix(0, nrow = 6, ncol = 6)
gen <- null_mat
gen[c(4,5,6), c(1,2,3)] <- 1
spe <- gen
spe[4, c(2,3)] <- spe[5, c(1,3)] <- spe[6, c(1,2)] <- 0

top_spe <- spe %>% rbind(., c(0, 0, 0, 1, 1, 1)) %>%
cbind(., rep(0, 7))

top_gen <- gen %>% rbind(., c(0, 0, 0, 1, 1, 1)) %>%
cbind(., rep(0, 7))

top_omn_spe <- top_spe
top_omn_spe[7, ] <- c(rep(1, 6), 0)

top_omn_gen <- top_gen
top_omn_gen[7, ] <- c(rep(1, 6), 0)

repl_module <- c(
  "spe" = "Specialist",
  "gen" = "Generalist",
  "top_spe" = "Top specialist",
  "top_gen" = "Top generalist",
  "top_omn_spe" = "Top omnivore\nspecialist",
  "top_omn_gen" = "Top omnivore\ngeneralist"
)
```

```{r}
par(mar = c(1.1, 1.1, 1.1, 1.1))

p_top_omn_gen <- ~PlotWeb(
  NetIndices::TrophInd(t(top_omn_gen))$TL,
  t(top_omn_gen),
  abund = rep(1, nrow(top_omn_gen)), colnode = "black")
p_top_omn_spe <- ~PlotWeb(
  NetIndices::TrophInd(t(top_omn_spe))$TL,
  t(top_omn_spe),
  abund = rep(1, nrow(top_omn_spe)), colnode = "black")
p_gen <- ~PlotWeb(
  NetIndices::TrophInd(t(gen))$TL,
  t(gen),
  abund = rep(1, nrow(gen)), colnode = "black")
p_spe <- ~PlotWeb(
  NetIndices::TrophInd(t(spe))$TL,
  t(spe),
  abund = rep(1, nrow(spe)), colnode = "black")
p_top_spe <- ~PlotWeb(
  NetIndices::TrophInd(t(top_spe))$TL,
  t(top_spe),
  abund = rep(1, nrow(top_spe)), colnode = "black")
p_top_gen <- ~PlotWeb(
  NetIndices::TrophInd(t(top_gen))$TL,
  t(top_gen),
  abund = rep(1, nrow(top_gen)), colnode = "black")

p_fw <- plot_grid(
  p_spe, p_gen,
  p_top_spe, p_top_gen,
  p_top_omn_spe, p_top_omn_gen,
  ncol = 2,
  label_size = 8,
  labels = repl_module
)
save_plot(
  here("report", "figures", "p_fw.pdf"),
  p_fw, ncol = 2, nrow = 3,
  base_asp = 1, base_height = 2)
```

```{r}
png(here("report", "figures", "spe_top_spe.png"),
  width = 480 * 1.618, height = 480, units = "px", bg = "transparent")
par(mfrow = c(1, 2))
PlotWeb(
  NetIndices::TrophInd(t(top_spe))$TL,
  t(top_spe),
  abund = rep(1, nrow(top_spe)), scale_abun = .3, colnode = "red")
title("Top generalist")
PlotWeb(
  NetIndices::TrophInd(t(spe))$TL,
  t(spe),
  abund = rep(1, nrow(spe)), scale_abun = .3, colnode = "green")
title("Specialist")
dev.off()
```

```{r}
gen_stab <- read_csv(here("generalism_stoch.csv"))

gen_stab %>%
  select(1:5) %>%
  mutate(
    stab_com = 1 / cv_com,
    fw = repl_module[fw]
    ) %>%
  pivot_longer(c(stab_com, avg_cv_sp, synchrony),
    names_to = "metric", values_to = "values") %>%
  ggplot(aes(x = fw, y = values)) +
  geom_boxplot()  +
  facet_wrap(~metric, scales = "free_y")
```

```{r}
p_gen_pred <- gen_stab %>%
  select(1:5) %>%
  filter(fw %in% c("spe", "top_spe")) %>%
  mutate(
    stab_com = 1 / cv_com,
    fw = c(
      "spe" = "Specialist\nconsumers",
      "top_spe" = "Generalist\ntop predator"
      )[fw]
    ) %>%
  pivot_longer(c(stab_com, avg_cv_sp, synchrony),
    names_to = "metric", values_to = "values") %>%
  mutate(metric = c("stab_com" = "Stability", "avg_cv_sp" = "Avg CVsp",
      "synchrony" = "Synchrony")[metric]) %>%
  ggplot(aes(x = fw, y = values, fill = fw)) +
  geom_boxplot() +
  labs(x = "Food web structure") +
  scale_fill_manual(values = c("red", "green")) +
  facet_wrap(~metric, scales = "free_y") +
  theme_cowplot(font_size = 14) +
  theme(
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "none"
  )

p_gen_pred

save_plot(
  here("report", "figures", "model_spe_top.png"),
  p_gen_pred,
  ncol = 3,
  base_asp = 1
)
```

### 2022-12-14 use_case/analysis_vasseur_fox.Rmd
Add simulations with some modules

mytheme <- theme_cowplot() +
background_grid()

@@

```{r}
data <- read_csv(here("res", "vasseur_fox_res.csv"))
colnames(data)[1:2] <- c("rho", "sigma") 
```
```{r}
avg  <- data %>%
  group_by(sigma, rho) %>%
  summarise(across(everything(), mean))
```

>>>>

mytheme <- theme_cowplot(font_size = 12) +
  background_grid() +
  theme(legend.position = "bottom")

@@

# Some simulations with stochasticity

```{r}
sim <- read_csv(here("use_case", "vasseur_fox_sim_ts_ex.csv")) %>%
  pivot_longer(c(resource:pred), names_to = "species", values_to = "bm") %>%
  mutate(species = str_replace_all(species, c(
        "pred" = "Predator",
        "cons1" = "Consumer 1",
        "cons2" = "Consumer 2",
        "resource" = "Resource"
        )))

sim0 <- sim %>%
  filter(sigma == 0)
unique(sim$sigma)
unique(sim$rho)
```

```{r}
p0 <- sim %>%
  filter(sigma == 0) %>%
  ggplot(aes(x = time, y = bm, color = species)) +
  geom_line()
save_plot(
  filename = here("use_case", "int_mccann_brose", "figures", "mccann_sim.png"),
  p0)
p_stoch <- sim %>%
  filter(sigma == 0.3, rho == 0.0) %>%
  ggplot(aes(x = time, y = bm, color = species)) +
  geom_line()
p_stoch_rho <- sim %>%
  filter(sigma == 0.3, rho == 1) %>%
  ggplot(aes(x = time, y = bm, color = species)) +
  geom_line()
```

```{r}
```

# Reproduce Vasseur & Fox

```{r}
data <- read_csv(here("res", "vasseur_fox_res.csv"))
colnames(data)[1:2] <- c("rho", "sigma")
```

```{r}
avg  <- data %>%
  group_by(sigma, rho) %>%
  summarise(across(everything(), mean))
```
